Appendix for 'Framing Effects in the Wild

### 2022-09-29 paper/appendix.Rmd
Adjust plot placement

---
title: "Appendix for 'Framing Effects in the Wild'"
author: "Nicolai Berk"
date: "15 5 2022"
output: 
  pdf_document:
    number_sections: TRUE
toc: TRUE
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, 
                      fig.width=10, fig.align='center', fig.pos = "!ht", out.extra = "")

@@

GroupedDistPlot("mip_mig",
                header = "Mention of Migration as Most Important Problem")

@@

@@

Annotation took place in a shiny app (see screenshot below). Coders were shown the title and text of a random news article in the sample. Then they were asked whether the article refers to the topics of crime, law and order, or public safety. Coders could see a more specific definition by clicking a button. After selecting whether the article referred to crime or not, they could either click a button to get to the next article or safe their progress to return later. Coders could also return to the preceding article in case they had selected the wrong option. The app allowed for faster annotation and minimized errors in the coding (compared to noting the annotations in an excel sheet).

```{r, fig.cap="Screenshot of Annotation App"}

@@

@@

# correlation table - not so great
table(common_nat$crime, common_rob$crime)

@@

The migration annotation has been conducted by only one coder (1800 articles), while the crime articles have been annotated by two different coders separately (1000 each with 200 identical articles in each coder's sample). Annotation was very reliable with an agreement for `r agreement`% of annotated articles and a Krippendorff's alpha of `r round(k_alpha, 2)`. Conflicts were resolved by the author after inspection of the conflicting codings.

### Classifier Training

```{=tex}
\begin{table}
\centering
\begin{tabular}{|p{12cm}|}
\hline
Final new years eve report of Cologne police: male groups identified \\ \hline
Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
Search in refugee home - mega-raid addressing asylum fraud \\ \hline
Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
\end{tabular}
\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
\label{tab:exampleArticles}
\end{table}
```

@@

## Salience of Migration

@@

## Treatment Groups

@@

Figure \@ref(fig:parallelTrends) shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel [@SOURCE]. This is a far smaller sample with a limited time frame and hence less useful for the precise estimation of the effects of changing migration framing. The plot shows that both groups move along a similar long-term trend, slowly becoming more conservative, while moving into similar directions along the way. The only difference between the two groups is that Bild readers seem to be more conservative in late 2015 (note that only the last three interviews were conducted in January 2016). However this deviation lies well within the 95% confidence interval and those not reading Bild move in a similar direction, albeit less strongly. The parallel trends assumption seems to be generally met.

```{r parallelTrends, fig.cap = "Migration Attitude among Bild-readers compared to non-readers across Time"}

@@

@@

```{r did_imm_att, results='asis'}

@@

## Longterm-Panel Model

@@

```{r LTPDiD, fig.height=2}

LTPDiD()

@@

```{r LTPDiD_table, results='asis'}

modelsummary::modelsummary(LTPDiD(return_table = T), output = "latex", stars = T)

@@

```{r did_cond_crime, results='asis'}

@@

```{r inselection}

@@

Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95% confidence intervals, dashed (red) vertical line indicates editorial change.

### Crowding out

```{r crowdout}

CrowdOutEstimates(vis = T)

>>>>

---
title: "Appendix for 'Framing Effects in the Wild'"
author: "Nicolai Berk"
date: "15 5 2022"
output: 
  bookdown::pdf_document2:
    number_sections: TRUE
toc: TRUE
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, 
                      fig.width=10, fig.align='center', fig.pos = "!htp", out.extra = "")

@@

gles_p_long[["dv"]] <- gles_p_long[["mip_mig"]]

p_upper <- 
  gles_p_long %>% 
  filter(treat, !is.na(dv)) %>% 
  ggplot(aes(dv)) +
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill = MetBrewer::met.brewer("Archambault")[4]) +
  theme_minimal() +
  xlab("") + ylab("Share") +
  ggtitle("Mention of Migration as Most Important Problem", "Bild Readers")

p_lower <- 
  gles_p_long %>% 
  filter(!treat, !is.na(dv)) %>% 
  ggplot(aes(dv)) +
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill = MetBrewer::met.brewer("Archambault")[1]) +
  theme_minimal() +
  xlab("") + ylab("Share") +
  ggtitle("", "Never Bild Readers")

p_upper / p_lower

rm(gles_p_long)

@@

rm(gles_p_long)

@@

```{r, fig.cap="Screenshot of Annotation App", out.width = "\\textwidth"}

@@

Annotation took place in a shiny app (see screenshot above). Coders were shown the title and text of a random news article in the sample. Then they were asked whether the article refers to the topics of crime, law and order, or public safety. Coders could see a more specific definition by clicking a button. After selecting whether the article referred to crime or not, they could either click a button to get to the next article or safe their progress to return later. Coders could also return to the preceding article in case they had selected the wrong option. The app allowed for faster annotation and minimized errors in the coding (compared to e.g. noting the annotations in an excel sheet).

@@

@@

The migration annotation has been conducted by only one coder (1800 articles), while the crime articles have been annotated by two different coders separately (1000 each with 200 identical articles in each coder's sample). Annotation was very congruent across coders with an agreement for `r agreement`% of annotated articles and a Krippendorff's alpha of `r round(k_alpha, 2)`. Conflicts were resolved by the author after inspection of the conflicting annotations.

\pagebreak

### Classifier Fine-tuning

bert_ests_raw <- 
    fread(here('data/processed/bert_crime_clean.csv'))

Using the annotated samples, I fine-tune BERT classifiers from Huggingface's 'transformers' library for python (bert-base-german-cased), pre-trained on german Wikipedia articles, legal documents, and news articles.  For each topic (crime/migration), 1400 articles served as training set, 200 each as validation and test set. Articles longer than 512 tokens (the maximum length of input for the BERT model) were truncated. I fine-tune for 10 epochs. Performance on the test set is outstanding for the migration classifier (F1 = 0.94, accuracy = 0.96, precision = 0.95, recall = 0.93) and very good for the crime classifier (F1 = 0.86, accuracy = 0.93, precision = 0.8, recall = 0.92). Both classifiers were subjected to sanity checks, before classifying first all articles according to their migration content, which returns `r nrow(bert_ests_raw)` articles (3.6% of all articles). For this subset, crime content is identified in `r sum(bert_ests_raw$crime_label)` articles (`r round(sum(bert_ests_raw$crime_label)/nrow(bert_ests_raw), 3)*100`).

```{=tex}
\begin{table}[!h]
\centering
\begin{tabular}{|p{12cm}|}
\hline
Final new years eve report of Cologne police: male groups identified \\ \hline
Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
Search in refugee home - mega-raid addressing asylum fraud \\ \hline
Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
\end{tabular}
\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
\label{tab:exampleArticles}
\end{table}
```

As a sanity check, and in order to exemplify the nature of the treatment, table \@ref(tab:exampleArticles) shows the five *Bild* articles classified as crime with the highest likelihood, out of all migration-related articles. All articles relate to both migration and crime: one mentions a police report on the mass sexual assaults on new years eve 2015 in Cologne, two discuss police raids in refugee homes, and two discuss violence in refugee shelters.

\pagebreak

@@

```{r migSalience, fig.cap="Attention to Migration in Different News Outlets"}

MigSaliencePlot()

Figure \@ref(fig:migSalience) shows that the prevalence of migration content as classified by the first Bert model generally follows expectations. Three distinct peaks can be observed: first during the migratory movements to Germany in 2015, then after the sexual assaults on new years eve in 2016, and during the conflict regarding migration policy within the conservative party alliance CDU/CSU in 2018. Prevalence differs strongly across newspapers, with *Bild* having the lowest prevalence of migration content. This is likely due to their tabloid format, which emphasizes entertainment over news and politics content. The left-leaning SZ shows the highest attention to migration (during the peak in September 2015, nearly every second article is concerned with migration). This is likely the result of a website highly focused on politics.

\pagebreak

@@

@@

```{r parallelTrends, fig.cap="Migration Attitude among Bild-readers compared to non-readers across Time"}

@@

Figure \@ref(fig:parallelTrends) shows the development of migration attitudes among a panel of Bild readers\footnote{Readership was measured in a single wave in late 2015.} and non-readers across time, recorded in the German Longitudinal Election Study's Longterm Panel [@GLES2018LangfristPanel]. This is a far smaller sample with a limited time frame and hence less useful for the precise estimation of the effects of changing migration framing. The plot shows that both groups move along a similar long-term trend, slowly becoming more conservative, while moving into similar directions along the way. The only difference between the two groups is that Bild readers seem to be more conservative in late 2015 (note that only the last three interviews were conducted in January 2016). However this deviation lies well within the 95% confidence interval and those not reading Bild move in a similar direction, albeit less strongly. The parallel trends assumption seems to be generally met.

\pagebreak

@@

```{r did_imm_att}

@@

DiDPlot(return_table = T, multi = T)

\pagebreak

@@

It is also possible to estimate the effect of the change in editorship from the smaller and less frequent long-term panel, with a smaller sample size (between 1,700 and 5,000). The only post-treatment wave has been conducted from September to December 2017. The question wording of the variable measuring immigration attitudes is identical to the Panel study used in the main paper, however responses have been recorded on a 11-point scale. Treatment was defined similar to the main paper, with respondents who indicated to read *Bild* in the pre-treatment wave in the treatment group, and respondents indicating never to read *Bild* in the control group.

```{r LTPDiD_table, fig.cap="Effect of Reichelt Takeover on Immigration Attitudes among Bild-reader"}

rawmodel <- LTPDiD(return_table = T)

delta_pt <- rawmodel$coefficients[["postTRUE:treatTRUE"]]
delta_lower <- confint(rawmodel)["postTRUE:treatTRUE", 1]
delta_upper <- confint(rawmodel)["postTRUE:treatTRUE", 2]

modelsummary::modelsummary(LTPDiD(return_table = T), output = "markdown", stars = T)

@@

The model suggests a liberalizing effect of `r round(delta_pt, 2)` (`r abs(round(delta_pt, 3))/10*100`% of the scale range), which is not significant (lower CI `r round(delta_lower, 2)`; upper CI `r round(delta_upper, 2)`), suggesting a null effect, similar to the main model.

\pagebreak

@@

```{r did_cond_crime}

@@

```{r inselection, fig.cap="Coefficients of OLS regression of readership on migration attitude across waves. Vertical lines indicate 95 percent confidence intervals, dashed (red) vertical line indicates editorial change."}

@@

# Resources
